Capstone Movielens Report

### 2025-11-10 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for functions: mean_reg, train_user_movie_effect.

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) script on _GitHub_.
:::

#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
\

Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda] argument. We will call it the _penaized mean_.

@@

::: { #func.mean_reg.args.vals .sidebar }
  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;

:::
::: { #func.mean_reg.args.lambda .sidebar }
  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.

@@

When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
$$
\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
$$

@@

The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
```{r eval=FALSE}
mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
  if (is.na(lambda)) {
    stop("Function: mean_reg
`lambda` is `NA`")
  }

@@

::: {.noteblock data-latex=""}
The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
:::
:::

>>>>

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) script on _GitHub_.
:::

#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
\

Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.

@@

::: { #func.mean_reg.args.vals .sidebar }
  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;

:::
::: { #func.mean_reg.args.lambda .sidebar }
  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.

@@

When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
$$
\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
$$

@@

The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
```{r eval=FALSE}
mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
  if (is.na(lambda)) {
    stop("Function: mean_reg
`lambda` is `NA`")
  }

@@

::: {.noteblock data-latex=""}
The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
:::
:::
